Notes on scheduling the SAA2019 meeting

### 2017-11-04 analysis/paper/saa2018_posters.Rmd
got the while loop going for posters

@@

We have information about how many posters can go into each session

@@

@@

# put out the after hours sessions and posters in a CSV
after_hours_poster_sessions_all_posters <- 
  org_and_after_hours_posters_individual %>% 
  filter(`Session Id` %in% after_hours_poster_sessions_only$`Session Id`) %>% 
  mutate(poster_session_time = "Th-evening")

write_csv(after_hours_poster_sessions_all_posters,
          "../data/derived_data/after_hours_poster_sessions_all_posters.csv")

@@

  # we're going to change these
  gen_and_org_poster_sessions_only_tmp <- gen_and_org_poster_sessions_only
  container_for_this_day_part <- 0
  poster_session_durations_summary$numbers_of_posters <- 0
  poster_session_durations_summary$n_posters <- 0
  poster_session_durations_summary$n_sessions <- 0
  poster_session_durations_summary$c_sessions <- 0
  i <- 1

@@

  # need a buffer
  buffer <- 10
  target_capacity <- poster_session_durations_summary$`N max`[i] - buffer

@@

      #  what if we remove the condition that there shoudl not be a clash with papers?
      names_already_in2 <- 0

@@

 poster_session_durations_summary$c_sessions[i] <-  sum(poster_session_durations_summary$n_sessions)

 print(poster_session_durations_summary %>% select(`N max`, 
                                                   day_part,
                                                   n_posters,
                                                   n_sessions, 
                                                   c_sessions))

@@

>>>>

after_hours_poster_sessions_all_posters <- 
  org_and_after_hours_posters_individual %>% 
  filter(`Session Id` %in% after_hours_poster_sessions_only$`Session Id`) %>% 
  mutate(poster_session_time = "Th-evening")

@@

We have `r nrow(n_ah_poster_sessions)` sessions of after-hours posters, for a total of `r nrow(after_hours_poster_sessions_all_posters)` posters.

We have `r nrow(gen_and_org_poster_sessions_only)` sessions of general and organised session posters, for a total of `r nrow(gen_and_org_poster_session_posters)` posters.

We have from the SAA information about how many posters can go into each session

@@

There are spaces for a total of `r sum(poster_session_durations$'N max')` posters. We have received `r nrow(gen_and_org_poster_session_posters)` poster submissions. So we have `r nrow(gen_and_org_poster_session_posters) - sum(poster_session_durations$'N max')` more posters than available spaces.

@@

# put out the after hours sessions and posters in a CSV
write_csv(after_hours_poster_sessions_all_posters,
          "../data/derived_data/after_hours_poster_sessions_all_posters.csv")

@@

  # we're going to change these
  gen_and_org_poster_sessions_only_tmp <- gen_and_org_poster_sessions_only
  container_for_this_day_part <- 0
  poster_session_durations_summary$numbers_of_posters <- 0
  poster_session_durations_summary$n_posters <- 0
  poster_session_durations_summary$n_sessions <- 0
  poster_session_durations_summary$c_sessions <- 0
  poster_session_durations_summary$c_posters <- 0
  all_of_the_day_parts <- 0
  i <- 1

@@

  # need a buffer
  buffer <- 3
  target_capacity <- poster_session_durations_summary$`N max`[i] - buffer

@@

@@

 poster_session_durations_summary$c_sessions[i] <-  sum(poster_session_durations_summary$n_sessions)
 poster_session_durations_summary$c_posters[i] <-  sum(poster_session_durations_summary$n_posters)

 print(poster_session_durations_summary %>% select(`N max`, 
                                                   day_part,
                                                   n_posters,
                                                   n_sessions, 
                                                   c_sessions,
                                                   c_posters))

@@

Seems that we have too many posters for the available space. Let's double-check:

```{r}
# duplicates?
all_of_the_day_parts %>% 
  distinct()

posters_with_abstract_ids <- 
all_of_the_day_parts %>% 
  filter(!is.na(`Abstract Id`)) %>% 
  group_by(day_part_from_while) %>% 
  tally() %>% 
  summarise(sum(n)) %>% 
  pull()
```

We have `r posters_with_abstract_ids` posters with Abstract IDs (and so not chair/co-chairs). Compare to `r nrow(gen_and_org_poster_session_posters)` posters that we started with, and space available for `r sum(poster_session_durations$'N max')` posters.
